A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Add threats to validity

\section{Threats to Validity}

>>>>

\section{Threats to Validity}
The primary threat to validity is the issue of code coverage, a cause of concern
for any dynamic approach. We mitigate this by including only those R packages in
our corpus that have many reverse dependencies and thus high code coverage.
Secondly, we turn off the bytecode compiler for this study. The bytecode
compiler can also call eval. Thirdly, we do not get source locations for
\missingNumber eval calls. These are the calls in which eval is passed as an
argument to a higher-order functions and the R parser does not retain location
information for them. However, this is a meager \missingPercentage of all eval
calls and is unlikely to affect our analysis.
